Distrivia: A Distributed Trivia Game

### 2011-04-22 papers/phase-two/paper.tex
Fix typos, add more about round robin dns, UI -> user interface

%\title{ Distributed Systems: Project Description }
\title{ Distrivia: A Distributed Trivia Game }
\numberofauthors{3}
\author{
\alignauthor
Brian Gianforcaro \\
       \affaddr{Rochester Institue of Technology}\\
       \email{bjg1955@rit.edu}
\alignauthor
Steven Glazer \\
       \affaddr{Rochester Institue of Technology}\\
       \email{sfg6126@rit.edu}
\alignauthor
Samuel Milton \\
       \affaddr{Rochester Institue of Technology}\\
       \email{srm2997@rit.edu}
}
\maketitle

@@

\subsection {Traffic}
We have two load sharers set up. Both sharers are currently configured to
divide the requests among the three active servers and, if need be, the two hot spares. The duplicate sharers allow
for a load distributer to go down and we would still be able to serve requests
to the servers. These load sharers are selected by the clients using round
robin DNS where distrivia.lame.ws will select either load distributer that is
up at random. This provides us will stability for access to the servers. The
load sharers are setup to attempt to connect to a server twice before
deeming it dead and removing it from its list of servers to direct clients towards.
Currently we are using the NGINX \cite{nginx} in a reverse proxy configuration
for our load sharing needs.

@@

\subsection {Messages}
We are currently using the https protocol for our messages. This provides a secure
and usable messaging system that we have designed our client and server APIs to use.
The actual messages are sent and received in two way's. Initially a user session key is
generated using the UUID \cite{uuid} algorithm and returned to the user on successful
authentication. This session key is then passed back to the server with every in coming
message. Messages are sent to the server using POST and GET request methods supported
by the HTTP protocol. Responses from the server are in the form of JSON \cite{json} objects.
JSON is a small, easily parseable format, representing objects in a human readable format as
they would be represented in JavaScript. With the web client the JSON object returned from
the server is instantly usable, however for the Android client we have to parse the JSON object
into a native Java object. The Android SDK provides libraries to do this, located in the
org.json \cite{orgjson} package name space.

\section {What's Left}
\subsection {Server}
The server is nearly completed. The server application just needs to have some tweaks and further testing.
\subsection {Web Client}
A lot of the main features of the web client are completed.
However, there are still a few remaining features that need to be implemented.
The only major feature remaining is private games, which are largely unstarted, although it will reuse most of the public game code.
In addition to this, buttons should be disabled when clicked to prevent users from spamming the server with repeat messages.
\subsection {Android}
Private gameplay is the largest thing left for the Android client. Besides this we've just been fixing bugs and cleaning up the UI.
\subsection {iPhone}
The iPhone application just started development in the last couple days. We have built most of the UI but need to connect all of the actions
to the server. We will need to implement everything, including login/registration, joining public/private games, viewing leaderboards,
and competing in rounds.

@@

Our system has three unique clients. One of them is designed for the Android platform as an app.
Another is designed for the iPhone platform as a native app.
The third is a web client, which is specifically being tested on Desktop and Laptop
browsers, however it may work on many hand held web browsers as well.

>>>>

%\title{ Distributed Systems: Project Description }
\title{ Distrivia: A Distributed Trivia Game }
\numberofauthors{3}
\author{
\alignauthor
Brian Gianforcaro \\
       \affaddr{Rochester Institute of Technology}\\
       \email{bjg1955@rit.edu}
\alignauthor
Steven Glazer \\
       \affaddr{Rochester Institute of Technology}\\
       \email{sfg6126@rit.edu}
\alignauthor
Samuel Milton \\
       \affaddr{Rochester Institute of Technology}\\
       \email{srm2997@rit.edu}
}
\maketitle

@@

\subsection {Traffic}
We have two load sharers set up. Both sharers are currently configured to
divide the requests among the three active servers and, if need be, the two hot spares. The duplicate sharers allow
for a load distributer to go down and we would still be able to serve requests
to the servers. These load sharers are selected by the clients using round
robin DNS where distrivia.lame.ws will select either load distributer that is
up at random. If a load distributer should go down or become unreachable the
DNS service will no longer serve that hosts DNS record until it is again
reachable. This provides us with stability for accessing the servers. The
load sharers are setup to attempt to connect to a server twice in a one second
period before deeming it dead and removing it from its list of servers to direct clients towards.
Currently we are using the NGINX \cite{nginx} in a reverse proxy configuration
for our load sharing needs.

@@

\subsection {Messages}
We are currently using the https protocol for our messages. This provides a secure
and usable messaging system that we have designed our client and server APIs to use.
The actual messages are sent and received in two way's. Initially a user session key is
generated using the UUID\cite{uuid} algorithm and returned to the user on successful
authentication. This session key is then passed back to the server with every in coming
message. Messages are sent to the server using POST and GET request methods supported
by the HTTP protocol. Responses from the server are in the form of JSON \cite{json} objects.
JSON is a small, easily parseable format, representing objects in a human readable format as
they would be represented in JavaScript. With the web client the JSON object returned from
the server is instantly usable, however for the Android client we have to parse the JSON object
into a native Java object. The Android SDK provides libraries to do this, located in the
org.json \cite{orgjson} package name space.

\section {What's Left}
\subsection {Server}
The server is nearly completed. The server application just needs to have some tweaks and further testing.
\subsection {Web Client}
A lot of the main features of the web client are completed.
However, there are still a few remaining features that need to be implemented.
The only major feature remaining is private games, which are largely unstarted, although it will reuse most of the public game code.
In addition to this, buttons should be disabled when clicked to prevent users from spamming the server with repeat messages.
\subsection {Android}
Private game play is the largest thing left for the Android client. Besides this we've just been fixing bugs and cleaning up the
user interface.
\subsection {iPhone}
The iPhone application just started development in the last couple days. We
have built most of the user interface but need to connect all of the actions
to the server. We will need to implement everything, including login/registration, joining public/private games, viewing leaderboards,
and competing in rounds.

@@

Our system has three unique clients. One of them is designed for the Android
platform as an application.
Another is designed for the iPhone platform as a native application.
The third is a web client, which is specifically being tested on Desktop and Laptop
browsers, however it may work on many hand held web browsers as well.
